Gravitational waves from colliding black holes

### 2017-04-24 Report/Draft/draft.tex
Reporting

\documentclass[]{article}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\bibliographystyle{unsrt}
\textwidth=430pt
\textheight=640pt
\hoffset=-50pt
\voffset=-80pt
%opening
\title{Gravitational waves from colliding black holes}
\author{Chris Pedersen}

\begin{document}
\maketitle
\begin{abstract}
A complete understanding of the LIGO detectors' ability to accurately measure spin parameters is of key importance to understanding the astrophysics of binary black hole systems. Of particular significance is an ability to determine spin orientations as a means of distinguishing between binary formation models. In this work we overview the core physics of gravitational waves, relativistic precession in binary systems, the LIGO detectors and the techniques involved in parameter estimation. We then examine the specific effects of precession on a gravitational waveform. The technique of 'matching' between waveforms is used as a computationally cheap way to explore degeneracies in the parameter space. A series of signals are then injected into simulated detector noise, and a full parameter estimation is performed on the data segments. Using the match results as a guide, we target these injections to areas in the parameter space where we expect to be particularly sensitive and insensitive to spin parameters. Inference for a full range of inclinations and phases is performed, and we identify areas where spin orientations are consistently incorrectly recovered. We then briefly examine the impact the upcoming VIRGO detector will have on spin estimation.

pdftotext draft.pdf - | wc -w 
\end{abstract}
\tableofcontents
\newpage

@@

\section{Precessing waveforms}

@@

\section{Matching}
Describe matching, and how matches are used to run targeted software injections.
Then identify parameter combinations where we are particularly sensitive to chi p, and those where we are not
\section{Software injections}

>>>>

\documentclass[11pt]{article}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\bibliographystyle{unsrt}
\textwidth=430pt
\textheight=640pt
\hoffset=-50pt
\voffset=-80pt
%opening
\title{Gravitational waves from colliding black holes}
\author{Chris Pedersen}

\begin{document}
\maketitle
\begin{abstract}
A complete understanding of the LIGO detectors' ability to accurately measure spin parameters is of key importance to understanding the astrophysics of binary black hole systems. Of particular significance is an ability to determine spin orientations as a means of distinguishing between binary formation models. In this work we overview the core physics of gravitational waves, relativistic precession in binary systems, the LIGO detectors, and the techniques involved in parameter estimation. We then examine the specific effects of precession on a gravitational waveform. The technique of 'matching' between waveforms is used as a computationally cheap way to explore degeneracies in the parameter space. A series of signals are then injected into simulated detector noise, and a full parameter estimation is performed on the data segments. Using the match results as a guide, we target these injections to areas in the parameter space where we expect to be particularly sensitive and insensitive to spin parameters. Inference for a full range of inclinations and phases is performed, and we identify areas where spin orientations are consistently incorrectly recovered. We then briefly examine the impact the upcoming VIRGO detector will have on spin estimation.
\end{abstract}
\tableofcontents
\newpage

@@

\section{Intrinsic degeneracies}
\subsection{Precessing waveforms}

@@

\subsection{Matching between waveforms}
An extremely useful and computationally cheap way to identify some of these degeneracies is through the process of matching as defined in (13). In the \textit{PyCBC} framework, the match is maximised over extrinsic parameters such as distance and source location that only affect the amplitude of a signal, and so is a useful tool for examining the similarities in the morphologies of different waveforms. A match takes values in the range $[0,1]$, with identical waveforms having a match of 1. Waveform template banks 
\subsection{Scanning the parameter space}
2D match plots
\section{Detector response simulations}
